\documentclass[overlapped,10pt]{res} % default is 10 pt
% margin option puts section titles to left of text
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{hyperref}



\begin{document}
\name{Brian Michael Bentson}

%

% the \\[12pt] adds a blank line after name
\address{    (650) 678-8889  \\ \textit{bmbentson@gmail.com}   \\ 
		}
%\address{ 
 	%	3432 Lodge Drive\\  Belmont CA, 94002 
	%	}
		


\begin{resume}


\section{EDUCATION}  



\normalsize{\bf M.S. Applied Mathematics, 2012 } 
\begin{itemize}  \itemsep -2pt % reduce space between items
 \item[] 
 California State University East Bay
\end{itemize} 
 
		
 
\normalsize{\bf B.S. Computational Mathematics, 2009 }
 
                \begin{itemize}  \itemsep -2pt % reduce space between items
                    
   		  \item[] 

 			University of California at Davis
                     
                    \end{itemize} 



   

		

\section{TECHNICAL COMPETENCIES} 



	           \begin{itemize} \itemsep -2pt % reduce space between items
                   \item[]  Python, PHP, Octave, LaTeX, Perl, MySQL, R, MATLAB, JavaScript, XML, HTML
                   \end{itemize}


 
\section{WORK EXPERIENCE}  


{\bf Hurricane Electric,  Fremont, CA } \\
                \begin{ncolumn}{2} % produces two equally spaced columns
                \underline{ Mathematician Web Developer}     &      1/2013-
                \end{ncolumn}
\begin{itemize} \itemsep -2pt
				  \item[] 
 	Designed and developed a mathematics e-learning web resource using mostly Python and PHP.
				  \item[] 
 Provided support for internal network operations along with assisting external transit, colocation and hosting companies.
               
					\end{itemize}   



{\bf Telenav,  Sunnyvale , CA } \\
                \begin{ncolumn}{2} % produces two equally spaced columns
                \underline{ Search Data Analyst Intern}     &      6/2011-4/2012
                \end{ncolumn}
\begin{itemize} \itemsep -2pt
				  \item[] 
 	Designed and developed a labeling\textbackslash evaluation system for use in machine learning systems in GPS search services under a LAMP environment.
				  \item[] 
 Cross-coordinated between search and content teams providing analysis of local search data mostly using R statistical language.
				 \item[]
Assisted Engineering team in white-box\textbackslash black-box testing of search systems.
 				
				\item[] 
 	Trained and Managed internal Content labelers.
  

               
					\end{itemize}   




{\bf Cengage Learning,  Belmont , CA } \\
                \begin{ncolumn}{2} % produces two equally spaced columns
                \underline{ Desktop Support Intern}     &      7/2010-9/2010  ,	4/2012-9/2012 
                \end{ncolumn}
\begin{itemize} \itemsep -2pt
				  \item[] 
 Created and maintained asset inventory databases.
				 \item[]
Assisted Engineering team in testing \& troubleshooting.
 				\item[] 
  Provided technical support for on \& off site staff.

               
					\end{itemize}   

  {\bf Bank of America,  Union City , CA } \\
                \begin{ncolumn}{2} % produces two equally spaced columns
                \underline{ Computer Operations Technician }     &      1/2010-6/2010
                \end{ncolumn}
\begin{itemize} \itemsep -2pt
				  \item[] 
 Maintained operation servers in a live environment .
				 \item[]
Assisted development team in troubleshooting.
 				\item[] 
  Provided technical support for on site staff.

               
					\end{itemize}   
		
	


\section{CERTIFICATIONS} 
$
\begin{array}{ccc} 

\textit{{\bf CompTIA} }
	      

&

\textit{ {\bf Federal Communications Commission} }
	         
&

\textit{ {\bf Stanford Online learning} }

\\
 \textit{Network+}
	      

&

 \textit{Technician Class Amateur Radio Operator}
	         
&

 \textit{Machine Learning}
	
 	
\end{array}
$

          	
   
\end{resume} 
\end{document}





